Titeltext

### 2018-07-24 thesis/paper/paper.tex
Added a small piece on datalog

\begin{document}
\chapter{Introduction/Preliminaries}
Motivation
\cite{test}
\section{Wikidata}
Wikidata is the knowledge base sister project of Wikipedia. It is a public, open database system that, at its core, stores statements about specific items. The basic unit of information is a triple subject-predicate-object stating an item (subject) has a property (predicate) which is either another item or a value of some kind (object). 
\chapter{Property Constraints}
To improve the data quality, help editors avoid common mistakes and clarify the usage of properties, Wikidata allows constraints to be defined on properties. They are however not firm rules and execptions can and should be made if necessary. A property constraint says something about the way a property may or may not be used. This can mean simple restrictions on the statement a property is part of, e.g. only certain values are allowed or more complex requirements on connected parts of the data graph, e.g. the value of a statement with this property should have certain statements. On the following page you can find table \ref{tab_basestats} which list the existing property constraints and a short description as well as classifying information which will be explained shortly. Afterwards the constraints will be explained in detail and either a basic approach for their modeling or reasoning why it is not possible or sensible to model it given.\\

>>>>

\begin{document}
\chapter{Introduction/Preliminaries}
Motivation
\cite{test}
\section{Wikidata}
Wikidata is the knowledge base sister project of Wikipedia. It is a public, open database system that, at its core, stores statements about specific items. The basic unit of information is a triple subject-predicate-object stating an item (subject) has a property (predicate) which is either another item or a value of some kind (object). 
\section{Datalog}
Datalog is a logic programming language. It is fully delarative and uses simple rules to derive additional knowledge from given facts. The most basic unit of information in datalog is a constant, which is a given [string]? expressing a fix point. In the context of Wikidata any entity or property, e.g. the universe (Q1) or head of government (P6), could be represented as a constant. Together with variables constants form terms. To form rules and define facts it is necessary to express their properties and relations. This is achieved using predicates
\chapter{Property Constraints}
To improve the data quality, help editors avoid common mistakes and clarify the usage of properties, Wikidata allows constraints to be defined on properties. They are however not firm rules and execptions can and should be made if necessary. A property constraint says something about the way a property may or may not be used. This can mean simple restrictions on the statement a property is part of, e.g. only certain values are allowed or more complex requirements on connected parts of the data graph, e.g. the value of a statement with this property should have certain statements. On the following page you can find table \ref{tab_basestats} which list the existing property constraints and a short description as well as classifying information which will be explained shortly. Afterwards the constraints will be explained in detail and either a basic approach for their modeling or reasoning why it is not possible or sensible to model it given.\\
